\chap{Conclusions}

\section{Summary}
\vspace{-5mm}
This course gave a lot of insight in the agile development process and how to split a large project between different team members. With user stories and specifications splitting the project into manageable parts, smaller pieces of code combines into a bigger application. In addition, using test driven development can help with making sure the code works like intended, without time-consuming manual testing.

\section{Further Works on the project}
\vspace{-5mm}
\begin{itemize}
\item \textbf{Smartphone application}\\ Even if the current web application is working properly using a smartphone browser, it would be interesting and useful to develop it as an application for current smartphone platforms (iOS, Android).
\item \textbf{Visibility of a timetable}\\
It could be useful to limit visibility of timetables with a privacy setting:
\vspace{-3mm}
\begin{itemize}
	\item Public: All the users can view and join the timetable.
	\item Private: A user can view and join the timetable only if they receive permission directly from the timetable's owner.
\end{itemize}
\item \textbf{Extra features to events}
\vspace{-3mm}
\begin{itemize}
	\item Description: Add a field during the creation of an event that allows the owner to add a description in order to provide more information about the event.
	\item Comments: Give users the possibility to add comments on an event that the user is following, for example, to ask questions.
	\item Follow a single event: Allow users to follow single events, without following the entire timetable.
\end{itemize}
\item \textbf{Integration with other platforms}
\vspace{-3mm}
\begin{itemize}
	\item Events: Export/import events to or from Facebook (Using Facebooks event feature) or Google Calendar.
	\item Accounts: Create and log in to an account using e.g. a Facebook or Google account.
\end{itemize}
\end{itemize}

\section{Further improvements on the teamwork}
\vspace{-5mm}
\begin{itemize}
 \item \textbf{Group coding} \\ Due to the team members having vastly different courses and schedules, there were not many chances to have dedicated coding sessions/workshops. Thus most of the programming of this application was done individually. However, the few coding sessions we did have, proved to be very enlightening and productive. \\Having more self-organized team workshops where programming was the main focus, in addition to the planning meetings we did have, could be very useful.\\
 %\item  \textbf{Division of features}\\As we created features to work on and different user stories, each team member would work on a specific part of the application. 
 
\end{itemize}